Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density \thanks{Based on observations collected at the La Silla Parana Observatory, ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}

### 2018-05-31 manuscript.tex
sec 4 updates

\xavier{In Fig.~\ref{fig:faculae.corr}, we compare the correlation between the different RV estimates and the different asymmetry or width estimates. As we can see, the strength of the correlation between $\gamma$ and SN mean RV, and $\gamma$ and SN median RV are much stronger than the correlations between BIS SPAN and RV, with Pearson correlation coefficient $R$ values of 0.46, -0.67 and -0.09, respectively. Regarding the width barycenter correlations, we also find a stronger correlation between SN FWHM and SN mean RV compared to the one between FWHM and RV, $R=0.98$ and 0.84, respectively. In this case however, the correlation between SN FWHM and SN median RV is smaller with $R=0.50$. This first analysis shows that in the case of a faculae, using some parameters from the SN can lead to much stronger correlation than the usual Normal parameters and therefore, the SN parameters seems to be better

probe better stellar activity. We will of course confirm this in the next sections presenting the case of a spot and of a spot plus a planet, but also in Sec~\ref{sec:4} when we will apply the SN fitting to real data sets.}

>>>>

Correlations between the different RV estimates and the different CCF asymmetry or width estimates are displayed in Fig.~\ref{fig:faculae.corr}. The strength of the correlation between $\gamma$ and SN mean RV, and $\gamma$ and SN median RV are stronger than the correlations between BIS SPAN and RV, with Pearson correlation coefficient $R$ values of 0.46, -0.67 and -0.09, respectively. For the width barycenter correlations, there is a stronger correlation between SN FWHM and SN mean RV compared to the one between FWHM and RV \jessi{updated to N mean RV?}, $R=0.98$ and 0.84, respectively. In this case however, the correlation between SN FWHM and SN median RV is smaller with $R=0.50$. This first analysis shows that in the case of a facula, using some parameters from the SN can lead to much stronger correlation than the usual Normal parameters and therefore, the SN parameters may better probe stellar activity. We investigate this feature further in the next sections where we consider simulated data with a single spot and a spot plus a planet, and in Sec~\ref{sec:4} with real observations.
